Visualisation of Brain Statistics with R-package `ggseg`

### 2019-04-15 draft_1_DVP.Rmd
Update draft_1_DVP.Rmd

Out-of-the-box, `ggseg3d()` works without supplying any extra information, and plots the `dkt_3d` atlas in 'LCBC' surface.
The 'LCBC' surface is the white matter surface, inflated in 10 steps, to increase visibility within folds of the brain, while still maintining curvature to indicate where folds have been.
All `[...]_3d` atlases have a built in `colour` column for default colour plotting of the segments.

@@

The cortical atlas data is stored in nested tibbles, which have datasets for three different surfaces and the two hemispheres.
The 'data'-column within includes all necessary information to `ggseg3d()` to create a mesh-plot. 
```{r, out.width='90%', size='small'}
dkt_3d
```

To grab all the data for a surface and hemisphere, you should reduce the data to one line, and then `unnest()`
```{r out.width='40%', linewidth=70}
dkt_3d %>% 
  filter(surf == "inflated" & hemi == "right") %>% 
  unnest(ggseg_3d) %>% 
  select(-lobe, -acronym)
```

### External data supply
Particularly notice the `mesh` column, which is a list column of lists. 
In there is all the 6 vectors needed to create the mesh of the tri-surface plot. 
You'll also need to notice the `label`, `annot` and `area` columns, which are likely the columns you will be matching on when proviging with your own data for colours. 
You need to be meticulous when fixing your data, be sure it matches.
The function _should_ give you a warning if it's struggling to match something.

@@

If you are plotting the sub-cortical structures, you might want to reduce the opacity of the `NA` structures, so that you can see the more medial structures. 
You may also want to add the `glassbrain` option, any value above 0 and up to 1 increases the opacity of a glass brain overlay.
The glassbrain option provides a frame of reference for the subcortical structures, and as such it is recommended to add this when viewing these structures.
There are three glassbrain options, controlling the opacity, which hemispheres to add, and the colour.

@@

There are many plotly options that may help you adapt the plot to look the way you wish. 
In addition to Carson Sievert's [book on plotly in R](https://plotly-book.cpsievert.me/), we recommend resources for [modifying axes in 3D plots](https://plot.ly/r/axes/#modifying-axes-for-3D-plots), the [basic introduction to tri-surface plots](https://plot.ly/r/trisurf/), and this tutorial on [tri-surface plots with plotly in R](https://moderndata.plot.ly/trisurf-plots-in-r-using-plotly/).

>>>>

Out-of-the-box, `ggseg3d()` plots the `dkt_3d` atlas in 'LCBC' surface.
The 'LCBC' surface consists on a semi-inflated white matter surface based on the _fsaverage_ template subject. See *SCRIPT* for reproducibility.
All `[...]_3d` atlases have a built in `colour` column for default colour plotting of the regions, based on the colorlut used in the neuroimaging sofware.

@@

The cortical atlas data is stored in nested tibbles. Each atlas have datasets for three different surfaces (see Figure X) and the two hemispheres.
The 'ggseg3d' column includes all necessary information to `ggseg3d()` to create a mesh-plot. 
The additional `[..._3d]` atlases in the ggsegExtra contain identical structures except for the subcortical atlases in which surface and hemisphere do not apply.

```{r, out.width='90%', size='small'}
dkt_3d
```

### External data supply
Similarly as in the 2D-atlas, the user will use ggseg3D to display through a color scale some descriptive or inferential statistics.
First, one needs to grab the data for a specific surface (and hemisphere, if desired) and then `unnest()` it.

```{r out.width='40%', linewidth=70}
dkt_3d %>% 
  filter(surf == "inflated" & hemi == "right") %>% 
  unnest(ggseg_3d) %>% 
  select(-lobe, -acronym)
```

Note the `mesh` column, which contains lists.
Each list corresponds to a regio and contains 6 vectors required to create the mesh of the tri-surface plot.

Note als the `label`, `annot` and `area` columns which provide matching values for your own data. 
Similarly to ggseg function, the label column should match the region names used in the original neuroimaging software while area and annot provide alternative/ secundary names. 
It is thus important to match your identifiers for region with those used in the atlas. 
A warning will be issued in case of any mismatch.

@@

Subcortical atlases include cortical surfaces and other landmark structures to visualization purposes only. 
One can control the opacity of the these `NA` structures, to improve visualization. 
Additionaly, one can add the `glassbrain` option, which provides a frame of reference for the subcortical structures.
Glassbrain can be controlled with thre different arguments: opacity (0-1), hemisphere (left, right), and colour.

@@

ggsed3d() are based on plotly and thus can be additional plotly functionalities will can be used to modify and improve the 3D atlas representations. 
In addition to Carson Sievert's [book on plotly in R](https://plotly-book.cpsievert.me/), we recommend resources for [modifying axes in 3D plots](https://plot.ly/r/axes/#modifying-axes-for-3D-plots), the [basic introduction to tri-surface plots](https://plot.ly/r/trisurf/), and this tutorial on [tri-surface plots with plotly in R](https://moderndata.plot.ly/trisurf-plots-in-r-using-plotly/).
Finally, we recommend [orca](https://github.com/plotly/orca#installation) command line to save ggseg3d atlas snapshots.
